\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex
adding more to heart project section

% TODO give this paragraph some more context so it doens't seem out of place
The way we incorporated branches into our workflow helped us collaborate in a
way that kept us organized. In general, if one of us was working on a specific
feature, we would create a branch with a name descriptive of that feature. This
methodology minimized difficult-to-resolve merge conflicts. We modeled this
workflow off of the ``Git Feature Branch Workflow'' Atlassian
tutorial~\autocite{atlassian}.
% TODO explain merge conflicts and cite that Atlassian thing

@@

\section{Supplies}
\label{sec:supplies}

@@

The goal of the project was to create an interactive model of a heart to teach
heart function to non-specialists, such as students in middle school. This meant
that the model had to be highly visual and simple to understand. Each visual
component would have to be designed in an intuitive fashion so that students
could begin interacting with the model without advanced knowledge of biology.

@@

We visited ``Den Den Town'' in Osaka in order to gather supplies we would need
in order to construct the heart. One of the most important purchases of this
trip was a two-meter long strip of Adafruit NeoPixel light emitting diodes
(LEDs). The design of this reel of LEDs enabled us to cut the strip at specific
points to create shorter strips. Each LED on the strip individually addressable,
allowing us to set the color of any LED along the strip. This perfectly suited
our needs for representing blood flow.

@@

The design for the interactive model is pictured in
Figure~\ref{fig:interactiveModel}. The most prominent feature of the model is
the plastic bottle containing the balloon. The volume of this balloon represents
the volume of the left ventricle. Instead of inflating the balloon with the air
compressor directly (pictured on the left of Figure~\ref{fig:interactiveModel},
we opted to pressurize a sealed two-liter soda bottle and suspend a balloon
inside. By pumping more air into the bottle, we could reduce the volume of the
balloon since the external pressure would be made greater than the internal
pressure; the balloon would shrink as a result. To accomplish switching the
flow of air, we designed a setup involving two valves.
% TODO do we need to cite something to explain the super simple physics of this?

\begin{figure}[h] \centering
    \includegraphics[width=0.7\textwidth]{interactive-model.png}
    \caption{A diagram representing the physical model of the heart}
    \label{fig:interactiveModel}
\end{figure}

Like the balloon which represents the volume of the left ventricle, the LED
strips represent both pressure and blood flow in different parts of the body.
Pressure is represented by color. The lower the pressure, the more blue the
lights will appear. By the same token, red represents high pressure. The LEDs
can display any color in between blue and red, so the light strips are often a
pinkish hue.

@@

The physical model also contains a digital number display, which can be seen in
the top right corner on Figure~\ref{fig:interactiveModel}.

@@

\begin{figure}[h] \centering
    \includegraphics[width=0.7\textwidth]{heart-gui.png}
    \caption{The GUI to enable five preprogrammed scenarios}
    \label{fig:heartGui}
\end{figure}

>>>>

% TODO give this paragraph some more context so it doens't seem out of place
The way we incorporated branches into our workflow helped us collaborate in a
way that kept us organized. In general, if one of us was working on a specific
feature, we would create a branch with a name descriptive of that feature. This
methodology minimized difficult-to-resolve merge conflicts. We modeled this
workflow off of the ``Git Feature Branch Workflow'' Atlassian
tutorial~\autocite{atlassian}.
% TODO explain merge conflicts

@@

Throughout our stay at Ritsumeikan, we also had the opportunity to work closely
with other Ritsumeikan students to create build a project that involved the
integration of hardware and software. With the help of students and professors
alike, we were able to produce an educational physical model of a heart
controlled by an Arduino microcomputer. Noma gave us tremendous assistance with
hardware. He taught us how to properly use the tools around the lab, and
purchased mechanical and electrical components we would need to complete our
task. Amano Sensei was always available to answer questions related to biology,
and helped us understand the mathematical model we would need to implement to
drive the physical model with software. We worked on this project every
Wednesday, completing the final model during the last week of our stay.
% TODO get the full name of Amano Sensei

@@

The goals and requirements of this project were set out by Haruo Noma, a
professor at Ritsumeikan University. The goal of the project was to create an
interactive model of a heart to teach heart function to non-specialists, such as
students in middle school. This meant that the model had to be highly visual and
simple to understand. Each visual component would have to be designed in an
intuitive fashion so that students could begin interacting with the model
without advanced knowledge of biology.

@@

\subsection{Supplies}
\label{sec:supplies}

With Noma Sensei as our guide, we visited ``Den Den Town'' in Osaka in order to
gather supplies we would need in order to construct the heart. One of the most
important purchases of this trip was a two-meter long strip of Adafruit NeoPixel
light emitting diodes (LEDs). The design of this reel of LEDs enabled us to cut
the strip at specific points to create shorter strips. Each LED on the strip
individually addressable, allowing us to set the color of any LED along the
strip. This perfectly suited our needs for representing blood flow.

% TODO give a citation about what an Arduino is
% TODO do we need citations about every microcomputer mentioned by name?
Noma Sensei had various microcomputers for us to experiment with in his lab,
including an obniz, an M5Stack, a Raspberry Pi and an Arduino. The Arduino was
the only computer that had a ``motor shield'' component which we believed would
be necessary for controlling the pumps.\footnote{In the end, we did not need
this component, since we abandoned the idea of taking apart a pump to drive the
DC motor directly.} Because of this, we chose the Arduino to be the core of the
physical model. This microcomputer ran the simulation and output data to the
various hardware components, such as the digital display, LED strips and switch
to control the air valves.

@@

The design for the interactive model is pictured in
Figure~\ref{fig:interactiveModel}. The most prominent feature of the model is
the plastic bottle containing the balloon. The volume of this balloon represents
the volume of the left ventricle. Instead of inflating the balloon with the air
compressor directly (pictured on the left of Figure~\ref{fig:interactiveModel}),
we opted to pressurize a sealed two-liter soda bottle and suspend a balloon
inside. By pumping more air into the bottle, we could reduce the volume of the
balloon since the external pressure would be made greater than the internal
pressure; the balloon would shrink as a result. To accomplish redirecting the
flow of air, we designed a setup involving two valves.
% TODO do we need to cite something to explain the super simple physics of this?

\begin{figure}[h] \centering
    \includegraphics[width=\textwidth]{interactive-model.png}
    \caption{A diagram representing the physical model of the heart}
    \label{fig:interactiveModel}
\end{figure}

Like the balloon which represents the volume of the left ventricle, the LED
strips represent both pressure and blood flow in different parts of the body.
Pressure is represented by color. The lower the pressure, the more blue the
lights will appear. Red represents high pressure. The LEDs can display any color
in between blue and red, so the light strips are often a pinkish hue.

@@

The physical model also contains a digital number display, which can be seen in
the top right corner on Figure~\ref{fig:interactiveModel}. The display shows the
number of the active scenario. Clicking on a scenario button in the GUI
(discussed in Section~\ref{sec:userInterfaceForHeartModel}) will change the
number being displayed.

@@

The red buttons along the top of the screen allow the user to toggle between
different scenarios. Each scenario also includes a helpful graphic below each
button.

\begin{figure}[h] \centering
    \includegraphics[width=\textwidth]{heart-gui.png}
    \caption{The GUI to enable five preprogrammed scenarios}
    \label{fig:heartGui}
\end{figure}

Not only can the GUI communicate with the Arduino; the Arduino can relay
information about the state of the model back to the GUI. The length of blue bar
on the left of Figure~\ref{fig:heartGui} corresponds to $f_{v}$ in the model,
while the blue bar on the right corresponds to $f_{1}$. On the physical model,
these values correspond to the rate of animation of both LED strips. The size of
the circle between the blue bars represents $V_{LV}$, the volume of the left
ventricle. Due to limitations about the accuracy with which we could control the
pump, the volume of the balloon does perfectly reflect the true value of
$V_{LV}$ in the model. By contrast, the radius of the graphic on-screen can be
set to be exactly proportional to the value of $V_{LV}$.

% TODO write about the final result of the heart model and include pictures
